\textbf{Are regime changes always bad economics? Evidence from daily financial data}

### 2019-05-15 doc/paper.tex
Typo corrections

\section{Data}
Political data are primarily drawn from the Center for Systemic Peace's (CSP) Polity IV Coup d'etat dataset and Coup d'etat Events handbook. The Coup d'etat dataset includes the date of 1) successful coups, 2) attempted coups, 3) plotted coups and 4) alleged coup plots. We focus on successful coups because it is difficult to classify failed coups.\footnote{\citet[p. 617]{needler1966political} has even gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting.''} The one exception is that we separately study the failed coup attempt in Venezuela in April 2002 in which the President of Venezuela, Hugo Chavez, was removed from office for two days because it provides a natural test\footnote{We refer to this as a natural test rather than a ``natural experiment'' as some definitions of natural experiments would imply as-if random assignment of each regime change to different groups of investors (see for example \citet{dunning2012natural}). While the events may appear ``random'' in the sense that they were unexpected by investors, a portion of investors was not randomly assigned into a pro-business regime regime change treatment group while others remained in control. This latter scenario is more aligned with many definitions of a natural experiment.} of the impact of the seemingly successful removal of a left-wing populist with a pro-business regime, and the ensuing reinstatement of a left-wing populist.

>>>>

\section{Data}
Political data are primarily drawn from the Center for Systemic Peace's (CSP) Polity IV Coup d'etat dataset and Coup d'etat Events handbook. The Coup d'etat dataset includes the date of 1) successful coups, 2) attempted coups, 3) plotted coups and 4) alleged coup plots. We focus on successful coups because it is difficult to classify failed coups.\footnote{\citet[p. 617]{needler1966political} has even gone so far as to say that ``the categories of coups that were aborted, suppressed, or abandoned melt into each other and into a host of other non-coup phenomena so as to defy accounting.''} The one exception is that we separately study the failed coup attempt in Venezuela in April 2002 in which the President of Venezuela, Hugo Chavez, was removed from office for two days because it provides a natural test\footnote{We refer to this as a natural test rather than a ``natural experiment'' as some definitions of natural experiments would imply as-if random assignment of each regime change to different groups of investors (see for example \citet{dunning2012natural}). While the events may appear ``random'' in the sense that they were unexpected by investors, a portion of investors was not randomly assigned into a pro-business regime change treatment group while others remained in control. This latter scenario is more aligned with many definitions of a natural experiment.} of the impact of the seemingly successful removal of a left-wing populist with a pro-business regime, and the ensuing reinstatement of a left-wing populist.
